---
title: "Model Output plots"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document: 
    toc: true
    toc_depth: 2
    number_sections: TRUE
    keep_tex: FALSE
params:
  report_location: offline # if report is being run within an environment in which a model run was already specified and that already has all                                flepmiop packages installed, "online", otherwise, "offline"
  opt: !r option_list = list(optparse::make_option(c("-c", "--config"), action="store", default=Sys.getenv("CONFIG_PATH", Sys.getenv("CONFIG_PATH")), type='character', help="path to the config file"), optparse::make_option(c("-d", "--data_path"), action="store", default=Sys.getenv("DATA_PATH", Sys.getenv("DATA_PATH")), type='character', help="path to the data repo"), optparse::make_option(c("-u","--run-id"), action="store", dest = "run_id", type='character', help="Unique identifier for this run", default = Sys.getenv("FLEPI_RUN_INDEX",flepicommon::run_id())),  optparse::make_option(c("-R", "--results-path"), action="store", dest = "results_path",  type='character', help="Path for model output", default = Sys.getenv("FS_RESULTS_PATH", Sys.getenv("FS_RESULTS_PATH")))) # parameter options that will be used if report ran "online". If "offline", options below will be used
  config: config_sample_2pop_inference.yml #name of configuration file
  model_output_dir: model_output #usually model_output, but if results were moved, might be different
  #results_path:  # path to the project folder within which the model_output directory lies. Comment out if current directory 
  #run_id: # name of the run_id to plot results for. Required if multiple run_ids in model_output. Comment out if only one run_id in config
  seir_modifier_scenario: Ro_all
  # name of the scenario to plot results for. Required if multiple scenarios in config. Comment out if no scecnarios in config
  outcome_modifier_scenario: test_limits
  # name of the scenario to plot results for. Required if multiple scenarios in config. Comment out if no scecnarios in config
  # NOTE: Eventually would want this to be able to plot multipe scenarios or run_ids on the same graphs?
  continue_on_error: yes
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(
	echo = FALSE,
	fig.align = "center",
	message = FALSE,
	warning = FALSE,
	cache = FALSE,
	cache.lazy = FALSE
)
# knitr::opts_knit$set(root.dir = opt$data_path)

```


```{r install-packages, include=FALSE}

# Only need to run this cell once. Takes quite a long time the first time, because downloads and installs many packages

if (params$report_location == "offline"){
  
  #  # set up an R environment using the packages that flepimop requires, so that they can be accessed by this notebook
  # suppressMessages(library(renv))
  # renv::init() # initialize R environment
  # file.copy("../flepimop/build/renv/renv.lock","renv.lock",overwrite = TRUE) # Note: currently this file is out of date - I actually had to copy from docker
  # renv::restore(exclude=c("config.writer","flepicommon","inference")) # update the R environment to include the flepimop required packages. Path to flepimop-custom packages is outdated so install these separately in next step
  
  # print("installing CRAN packages")
  # install.packages(c("devtools", "arrow", "tidyverse", "truncnorm", "cdlTools", "ggraph", "doParallel", "foreach", "tidygraph", "tigris", "xts", "optparse","data.table","covidcast"), dependencies = TRUE, repos = "http://cran.us.r-project.org")
  
  # from local install instructions on Github
  #install.packages(c("readr","sf","lubridate","tidyverse","gridExtra","reticulate","truncnorm","xts","ggfortify","flextable","doParallel","foreach","optparse","arrow","devtools","cowplot","ggraph"), dependencies = TRUE, repos = "http://cran.us.r-project.org")
  
  # 
  # # Install flepimop custom R packages first. See flepimop/flepimop/local_install.R, or simply run below
  # 
  # pkg.dir <- "../flepimop/flepimop/R_packages/"
  # 
  # #list of local packages (reorder so flepicommon is installed first)
  # loc_pkgs <- list.files(pkg.dir,full.names=TRUE)
  # loc_pkgs <- loc_pkgs[c(which(grepl("flepicommon", loc_pkgs)), which(!grepl("flepicommon", loc_pkgs)))]
  # 
  # # Install them
  # print("installing flepimop packages")
  # install.packages(loc_pkgs,type='source',repos=NULL, dependencies = TRUE)
  
}
 

suppressMessages(library(flepicommon))
suppressMessages(library(inference))
suppressMessages(library(parallel))
suppressMessages(library(foreach))
suppressMessages(library(tidyverse))
suppressMessages(library(tidyr))
suppressMessages(library(doParallel))
suppressMessages(library(dplyr))
suppressMessages(library(data.table))
suppressMessages(library(ggplot2))
suppressMessages(library(ggforce))
suppressMessages(library(ggforce))
suppressMessages(library(gridExtra))


```


```{r parameter-setup, include=FALSE}

if (params$report_location == "online"){
  parser=optparse::OptionParser(option_list=params$opt)
  opt = optparse::parse_args(parser, convert_hyphens_to_underscores = TRUE)
}else if (params$report_location == "offline"){
  opt <- params
}else{
  stop('params:report_location must be either online or offline')
}

#load configuration file
config <- flepicommon::load_config(opt$config)

# get the location of model_output file
res_dir <- paste0(ifelse(is.null(opt$results_path),"",paste0(opt$results_path,"/")), opt$model_output_dir)
print(res_dir)

# get the directory of the results for this config + scenario: {config$name}_{seir_modifier_scenario}_{outcome_modifier_scenario}
setup_prefix <- paste0(config$name,ifelse(is.null(config$seir_modifiers$scenarios),"",paste0("_",opt$seir_modifier_scenario)),ifelse(is.null(config$outcome_modifiers$scenarios),"",paste0("_",opt$outcome_modifier_scenario)))
#print(setup_prefix)

scenario_dir <-file.path(res_dir,setup_prefix)
print(scenario_dir)

# find all unique run_ids within model_output. Must choose one only for plotting
run_ids <- list.files(scenario_dir)
print(run_ids)

this_run_id <- ifelse(length(run_ids)==1,run_ids[1],ifelse(is.null(opt$run_id),stop(paste0('There are multiple run_ids within ',scenario_dir,'/, you must specify which one to plot the results for in the notebook header using params:run_id')),opt$run_id))
print(this_run_id)

# entire path to the directory for each type of model output
scenario_run_dir <- file.path(scenario_dir,this_run_id)

# detects whether this is an inference or non-inference config
inference <- ifelse(is.null(config$inference),FALSE,TRUE)

# detects whether seir parameter modifiers were run in config
eval_snpi <- ifelse(is.null(config$seir_modifiers),FALSE,TRUE)

# detects whether outcomes were specified in config
eval_hosp <- ifelse(is.null(config$outcomes),FALSE,TRUE)

# detects whether outcome parameter modifiers were included in config
eval_hnpi <- ifelse(is.null(config$outcome_modifiers),FALSE,TRUE)

```

```{r read-model-output}

# Function to read in any model output file type for inference or non-inference run

import_model_outputs <- function(scn_run_dir, inference, outcome, global_opt = NULL, final_opt = NULL, 
                                 lim_hosp = c("date", "incidC", "incidH", "incidD",subpop) # only used if outcome = 'hosp'
                                 # lim_hosp = c("date",sapply(1:length(names(config$inference$statistics)), function(i) purrr::flatten(config$inference$statistics[i])$sim_var)
){
  
  if(inference){ 
    
    if(is.null(global_opt) | is.null(final_opt)){
      stop("Inference run, must specify global_opt and final_opt")
    }else{
      inference_filepath_suffix <-paste0("/",global_opt,"/",final_opt)
    print(paste0('Assuming inference run with files in',inference_filepath_suffix))
    }
    
  }else{ # non inference run
    
   inference_filepath_suffix <-""
  print('Assuming non-inference run. Ignoring values of global_opt and final_opt if specified') 
    
  }
  
  subdir <- paste0(scn_run_dir,"/", outcome,"/",inference_filepath_suffix, "/")
  #print(subdir)
  subdir_list <- list.files(subdir)
  #print(subdir_list)
  
  out <- NULL
  total <- length(subdir_list)
  
  print(paste0("Importing ", outcome, " files (n = ", total, "):"))
  
  for (i in 1:length(subdir_list)) {
    
    if (outcome == "hosp") {
      dat <-
        arrow::read_parquet(paste(subdir, subdir_list[i], sep = "/")) %>%
        select(all_of(lim_hosp))
    }else{
      
      
    }
    
    # read in parquet or csv files
    if (any(grepl("parquet", subdir_list))) {
      dat <-
        arrow::read_parquet(paste(subdir, subdir_list[i], sep = "/"))
    } else if (any(grepl("csv", subdir_list))) {
      dat <- read.csv(paste(subdir, subdir_list[i], sep = "/"))
    }
    
    # if outcomes file, select only desired outcome columns
    if (outcome == "hosp") {
        dat <- dat %>% select(all_of(lim_hosp))
      }
    
    if(inference == TRUE & final_opt == "intermediate"){ # if an 'intermediate inference run', filename prefix will include slot, (block), and iteration number
      
      dat$slot <- as.numeric(str_sub(subdir_list[i], start = 1, end = 9))
      dat$block <-as.numeric(str_sub(subdir_list[i], start = 11, end = 19))
      dat$iter <-as.numeric(str_sub(subdir_list[i], start = 21, end = 29))
      
    }else{ # if a non-inference run or a 'final' inference run, filename prefix will only contain slot #. Each file is a separate slot
      
      dat$slot <- as.numeric(str_sub(subdir_list[i], start = 1, end = 9))
      
    }
    
    out <- rbind(out, dat)
    
  }
  return(out)
  
}
                        
```


```{r read-in-data}
# Pull in subpop data
geodata <-
  setDT(read.csv(file.path(
    config$data_path, config$subpop_setup$geodata
  )))
# geodata <- setDT(read.csv(file.path(config$data_path, config$subpop_setup$geodata)))


## gt_data MUST exist directly after a run (ONLY IF INFERENCE RUN)
if (!is.null(config$inference)) {
  gt_data <- data.table::fread(config$inference$gt_data_path) #%>%
    # .[, subpop := stringr::str_pad(FIPS,
    #                                width = 5,
    #                                side = "left",
    #                                pad = "0")]
}

theme_small <-
  theme(
    text = element_text(size = 8),
    strip.background = element_blank(),
    strip.placement = "outside"
  )

```


```{r rmd_formatting}
fig_counter <- 1
tab_counter <- 1
multi_fig_height <- length(unique(geodata$subpop))
```



Here is a snapshot 📸 of your model outputs for run ID `r this_run_id`, from config `r opt$config`, stored in `r opt$model_output_dir`. 



# Infection model: SEIR model output
These are the SEIR outputs for your infection model, showing infection states (aggregated across other strata).

```{r seir, results='hide',fig.keep='all'}
# read in model outputs
seir_outputs_global <-
  setDT(import_model_outputs(scenario_run_dir, inference, "seir", 'global', 'final'))

# get different aggregation from list of config compartments?
## assuming there is always infection_stage, aggregate over this, incorporate aggregation of other variables later TO DO and make general to whatever first stratification listed in config file is
## assume always interested in prevalence

# if(inference){group_by_cols <- c("mc_infection_stage", "mc_value_type","slot","date")}else{group_by_cols <- c("mc_infection_stage","mc_value_type","date")}
group_by_cols <-
  c("mc_infection_stage", "mc_value_type", "slot", "date") # I think if just one slot, gets read in as slot = 1?
subpop_cols <-
  colnames(seir_outputs_global)[!str_detect(colnames(seir_outputs_global), "mc")]
subpop_cols <-
  subpop_cols[which(!subpop_cols %in% c("date", "slot"))]

tmp_seir <- seir_outputs_global %>%
  .[, lapply(.SD, sum, na.rm = TRUE), by = group_by_cols, .SDcols = subpop_cols]

# plot an example simulation, from the first slot
print(
  tmp_seir %>% .[mc_value_type == "prevalence" &
                   slot == sample(unique(tmp_seir$slot), 1)] %>%
    data.table::melt(., measure.vars = subpop_cols) %>%
    ggplot() +
    geom_line(aes(date, value, colour = mc_infection_stage)) +
    facet_wrap(
      ~ variable,
      scales = 'free',
      ncol = 4,
      strip.position = "top"
    ) +
    labs(y="Prevalence",colour = "Infection stage") + 
    theme_classic() +
    theme(legend.position = "bottom") + 
    theme_small
)
```


# Outcome model: HOSP model output
<!-- if NO inference, just plot hosp at daily - all aggregate outcomes (?) -->
<!-- if inference, plot hosp with gt at daily, and at fitting aggregation - ONLY stats in the inference section? -->
<!-- cumulatives and incident for all? -->
<!-- plot quantiles and some sample trajectories as well -->
Here are the results from your outcomes model. If you ran more than one simulation, here's a randomly sampled simulation, and if you ran more, here are the quantiles of all your simulations. 

Note: this should be fixed to include all outcomes and no data - save that for later section with inference stuff

<!-- NOTE: this needs to be updated to account for fact that with inference, outcome variable doesn't need to have the same name for model and ground truth data -->
## Daily hosp single trajectories {.tabset}
```{r hosp_daily_single_slot, results='asis', eval = eval_hosp}

# get all outcome variables
list_of_vars_config <- "config$outcomes$outcomes"
outcomes <- eval(parse(text = list_of_vars_config))
outcome_vars <- names(outcomes)

# for simplicity, get aggregate outcome variables
outcome_vars_ <- outcome_vars[!str_detect(outcome_vars, "_")]

# read in model outputs
hosp_outputs_global <- setDT(import_model_outputs(scenario_run_dir, inference,  "hosp", 'global', 'final',
                                                  lim_hosp = c("date", "subpop", outcome_vars_)))
# lim_hosp = c("date", "subpop", outcome_vars_)))
num_nodes <- length(unique(hosp_outputs_global %>% .[,"subpop"])) 

sim_sample <- sample(unique(hosp_outputs_global$slot),1)

cat("\n\n")

## plot ONE sample trajectory for sanity check (can modify) 
for(i in 1:length(outcome_vars_)){
  
  cat(paste0("### ",outcome_vars_[i]," {.tabset} \n"))
  
  cat(paste0("#### Incident \n"))

  ## Incident 
  print(
    hosp_outputs_global %>%
      .[, date := lubridate::as_date(date)] %>%
      .[, .(date, subpop, outcome = get(outcome_vars_[i]), slot)] %>%
      .[slot == sim_sample] %>%
      #data.table::melt(., id.vars = c("date", "slot", "subpop")) %>%
      data.table::melt(., id.vars = c("date", "slot", "subpop")) %>%
      ggplot() + 
      geom_line(aes(x = date, y = value)) + 
      # if inference, plot gt along side
      {if(inference)
        if(outcome_vars_[i] %in% colnames(gt_data))
         if(any(!is.na(gt_data %>% .[, get(outcome_vars_[i])])))
           geom_point(data = gt_data %>% .[, .(date, subpop, value = get(outcome_vars_[i]))],
                      aes(lubridate::as_date(date), value), color = 'firebrick', alpha = 0.1)
      } +
      facet_wrap(~subpop, scales = 'free') +
      #facet_wrap(~get(subpop), scales = 'free') +
      labs(x = 'date', y = outcome_vars_[i], title = "Incidence") +
      theme_classic() + theme_small
  )
  
    cat("\n\n")

  cat(paste0("#### Cumulative \n"))
  
  ## Cumulative
  print(
    hosp_outputs_global %>%
      .[, date := lubridate::as_date(date)] %>%
      .[, .(date, subpop, outcome = get(outcome_vars_[i]), slot)] %>%
      .[slot == sim_sample] %>% 
      data.table::melt(., id.vars = c("date", "slot", "subpop")) %>%
      # dplyr::arrange(subpop, slot, date) %>% 
      #.[, csum := cumsum(value), by = .(slot, subpop, variable)] %>%
      .[, csum := cumsum(value), by = .(slot, subpop, variable)] %>%
      ggplot() + 
      geom_line(aes(x = date, y = csum)) + 
      {if(inference)
        if(outcome_vars_[i] %in% colnames(gt_data))
          geom_point(data = gt_data %>% .[, .(date, subpop, value = get(outcome_vars_[i]))] %>%
                      .[, csum := cumsum(value) , by = .(subpop)],
                    aes(lubridate::as_date(date), csum), color = 'firebrick', alpha = 0.1) 
      } +
      facet_wrap(~subpop, scales = 'free') +      
      #facet_wrap(~get(subpop), scales = 'free') +      
      labs(x = 'date', y = paste0("cumulative ", outcome_vars_[i]), title = "Cumulative") +
      theme_classic() + theme_small
  )
  
  
  cat("\n\n")
  
}

```

## Quantiles {.tabset}
```{r hosp_daily_quantiles, results='asis', eval = eval_hosp}
# ```{r hosp_daily_quantiles, fig.dim = c(8,8), results='hide',fig.keep='all'}

if(length(unique(hosp_outputs_global$slot)) > 1){
  
  cat("\n\n")
  
  ## plot quantiles (if more than one slot)
  for(i in 1:length(outcome_vars_)){
    
    cat(paste0("### ",outcome_vars_[i]," {.tabset} \n"))
    ## plot quantiles (if more than one slot)
    # for(i in 1:length(outcome_vars_)){
    
        cat(paste0("#### Incident \n"))
    # incident
    print(
      hosp_outputs_global %>%
        .[, date := lubridate::as_date(date)] %>%
        # .[, as.list(quantile(get(outcome_vars_[i]), c(.05, .25, .5, .75, .95), na.rm = TRUE, names = FALSE)), by = c("date", "subpop")] %>%
        .[, as.list(quantile(get(outcome_vars_[i]), c(.05, .25, .5, .75, .95), na.rm = TRUE, names = FALSE)), by = c("date", "subpop")] %>%
        setnames(., paste0("V", 1:5), paste0("q", c(.05,.25,.5,.75,.95))) %>%
        ggplot() + 
        geom_ribbon(aes(x = date, ymin = q0.05, ymax = q0.95), alpha = 0.1) +
        geom_ribbon(aes(x = date, ymin = q0.25, ymax = q0.75), alpha = 0.1) +
        geom_line(aes(x = date, y = q0.5)) + 
        # if inference, plot gt along side
        {if(inference & outcome_vars_[i] %in% colnames(gt_data))
          if(any(!is.na(gt_data %>% .[, get(outcome_vars_[i])])))
            geom_point(data = gt_data %>% .[, .(date, subpop, value = get(outcome_vars_[i]))],
                       aes(lubridate::as_date(date), value), color = 'firebrick', alpha = 0.1)
        } +
        facet_wrap(~subpop, scales = 'free') +
        #facet_wrap("subpop, scales = 'free') +
        labs(x = 'date', y = outcome_vars_[i], title = "Incidence") +
        theme_classic()+ theme_small
    )
    
    cat("\n\n")
    
    cat(paste0("#### Cumulative \n"))

    # cumulative
    print(
      hosp_outputs_global %>%
        .[, date := lubridate::as_date(date)] %>%
        .[, .(date, subpop, outcome = get(outcome_vars_[i]), slot)] %>%
        data.table::melt(., id.vars = c("date", "slot", "subpop")) %>%
        # dplyr::arrange(subpop, slot, date) %>% 
        .[, csum := cumsum(value), by = .(slot, subpop, variable)] %>%
        .[, as.list(quantile(csum, c(.05, .25, .5, .75, .95), na.rm = TRUE, names = FALSE)), by = c("date", "subpop")] %>%
        setnames(., paste0("V", 1:5), paste0("q", c(.05,.25,.5,.75,.95))) %>%
        ggplot() + 
        geom_ribbon(aes(x = date, ymin = q0.05, ymax = q0.95), alpha = 0.1) +
        geom_ribbon(aes(x = date, ymin = q0.25, ymax = q0.75), alpha = 0.1) +
        geom_line(aes(x = date, y = q0.5)) + 
        {if(inference & outcome_vars_[i] %in% colnames(gt_data))
          geom_point(data = gt_data %>% .[, .(date, subpop, value = get(outcome_vars_[i]))] %>%
                       .[, csum := cumsum(value) , by = .(subpop)],
                     aes(lubridate::as_date(date), csum), color = 'firebrick', alpha = 0.1) 
        } +
        facet_wrap(~subpop, scales = 'free') +      
        #facet_wrap(~get(subpop), scales = 'free') +
        labs(x = 'date', y = paste0("cumulative ", outcome_vars_[i]), title = "Cumulative") +
        theme_classic() + theme_small
    )
    
      cat("\n\n")

  }
  
}

```


# Infection model: SNPI model output
Here are the SEIR parameter modifiers for your model. If inference is run, parameters are coloured by their likelihoods in a given subpopulation. 

```{r snpi, results='hide',fig.keep='all',eval = eval_snpi} 
# read in model outputs
snpi_outputs_global <- setDT(import_model_outputs(scenario_run_dir, inference,  "snpi", 'global', 'final'))
#node_names <- unique(snpi_outputs_global %>% .[ , get(subpop)])
node_names <- unique(sort(snpi_outputs_global %>% .[ , subpop]))
node_names <- c(node_names[str_detect(node_names,",")], node_names[!str_detect(node_names,",")]) # sort so that multiple subpops are in front

if(inference){
  llik <- setDT(import_model_outputs(scenario_run_dir, inference,  "llik", 'global', 'final'))
  # snpi_outputs_global <- snpi_outputs_global %>%
  #   .[llik, on = c("subpop", "slot")] 
}

snpi_plots <- lapply(node_names,
                     function(i){
                       # print(i)
                       if(!grepl(',', i)){
                         snpi_outputs_global %>%
                           {if(inference)
                             .[llik, on = c("subpop", "slot")] else .} %>%
                           .[subpop == i] %>%
                           # .[subpop == "sample_state"] %>%
                           ggplot(aes(npi_name,reduction)) +
                           geom_violin() +
                           {if(inference)
                             geom_jitter(aes(group = npi_name, color = ll), size = 0.5, height = 0, width = 0.2, alpha = 0.5)
                           } +
                           {if(!inference)
                             geom_jitter(aes(group = npi_name), size = 0.5, height = 0, width = 0.2, alpha = 0.5)
                           } +
                           theme_bw(base_size = 10) +
                           theme(axis.text.x = element_text(angle = 60, hjust = 1, size = 6),
                                 text = element_text(size = 8),
                                 legend.key.size = unit(0.2, "cm")) +
                               # guides(color = guide_legend(override.aes = list(size = 0.5)))+
                           scale_color_viridis_c(option = "B", name = "log\nlikelihood") +
                           labs(x = "parameter", title = i) + theme_small
                           # print("finished 1")
                       }else{
                         if(inference){
                           nodes_ <- unlist(strsplit(i,","))
                           ll_across_nodes <-
                             llik %>%
                             .[subpop %in% nodes_] %>%
                             .[, .(ll_sum = sum(ll)), by = .(slot)]
                         }

                         snpi_outputs_global %>%
                           {if(inference)
                             .[ll_across_nodes, on = c("slot")] else .} %>%
                           # .[subpop == "sample_state"] %>%
                           .[subpop == i] %>%
                           ggplot(aes(npi_name,reduction)) +
                           geom_violin() +
                           {if(inference)
                             geom_jitter(aes(group = npi_name, color = ll_sum), size = 0.5, height = 0, width = 0.2, alpha = 0.5)
                           } +
                           {if(!inference)
                             geom_jitter(aes(group = npi_name), size = 0.5, height = 0, width = 0.2, alpha = 0.5)
                           } +
                           theme_bw(base_size = 10) +
                           theme(axis.text.x = element_text(angle = 60, hjust = 1, size = 6),
                                 text = element_text(size = 8),
                                 legend.key.size = unit(0.2, "cm")) +
                           scale_color_viridis_c(option = "B", name = "log\nlikelihood") +
                           labs(x = "parameter") + theme_small
                         
                         # print("finished 2")
                       }
                     }
)
if(length(snpi_plots)!=1){
  print(do.call("grid.arrange", c(snpi_plots, ncol=4)))
}else{
  print(snpi_plots[[1]])
}

```





# Outcome model: HNPI model output
This shows the parameters associated with your outcomes model, for all subpopulations. If inference is run, points are coloured by the associated likelihoods.

PROBLEM: Currently not working for non-inference runs

```{r hnpi, results='hide',fig.keep='all', eval = eval_hnpi}
# read in model outputs
hnpi_outputs_global <- setDT(import_model_outputs(scenario_run_dir, inference,  "hnpi", 'global', 'final'))
# node_names <- unique(hnpi_outputs_global %>% .[ , get(subpop)])
node_names <- unique(hnpi_outputs_global[,subpop])
node_names <- c(node_names[str_detect(node_names,",")], node_names[!str_detect(node_names,",")]) # sort so that multiple subpops are in front

if(inference){
  llik <- setDT(import_model_outputs(scenario_run_dir, inference,  "llik", 'global', 'final'))
}


hnpi_plots <- lapply(node_names,
                     function(i){
                       hnpi_outputs_global %>%
                         {if(inference)
                             .[llik, on = c("subpop", "slot")] else .}%>%
                         .[subpop == i] %>%
                         ggplot(aes(npi_name,reduction)) + 
                         geom_violin() +
                         {if(inference)
                           geom_jitter(aes(group = npi_name, colour = ll), size = 0.6, height = 0, width = 0.2, alpha = 1) 
                         } +
                         {if(!inference)
                           geom_jitter(aes(group = npi_name), size = 0.6, height = 0, width = 0.2, alpha = 1)
                         } + 
                         facet_wrap(~subpop, scales = 'free') +
                         scale_color_viridis_c(option = "B", name = "log\nlikelihood") +
                         theme_classic()+ theme_small+ theme(legend.key.size = unit(0.2, "cm"))
                     }
)
if(length(hnpi_plots)!=1){
  print(do.call("grid.arrange", c(hnpi_plots, ncol=4)))
}else{
  print(hnpi_plots[[1]])
}

```

# Inference: analyses
If you ran inference, here are some analyses that might be helpful!

## Likelihood
(This is not really correct since it's only pulling from global files, which only exist when a global acceptance happened? seems like some iterations missing)
```{r llik_acceptances, eval = inference}

llik_outputs_int <- setDT(import_model_outputs(scenario_run_dir, inference,  "llik", 'global', 'intermediate'))

# print(
#   llik_outputs_int %>% 
#     ggplot() + 
#     geom_line(aes(iter,accept_prob, group = as.factor(slot))) +
#     guides(colour = "none") + 
#     labs(x = 'iterations', y = "probability of acceptance") +
#     facet_wrap(~subpop) +
#   theme_classic() + theme_small
# )


# print(
#   llik_outputs_int %>% 
#   ggplot() + 
#   geom_line(aes(iter,accept_avg, group = as.factor(slot))) +
#   guides(colour = "none") + 
#   labs(x = 'iterations', y = "acceptance average") +
#   facet_wrap(~subpop) +
#   theme_classic() + theme_small
# )

llik_outputs_int %>% 
  pivot_longer(cols = c("ll","accept_avg","accept","accept_prob")) %>% ggplot() +
  geom_line(aes(iter, value, group = as.factor(slot))) + 
  facet_grid(name ~ subpop, scales = 'free_y')+
  labs(x = 'iterations', y = "llikelihood stats") +
  theme_minimal() + theme_small



```


## Inference specific outcomes: aggregated single trajectories {.tabset}

In your inference method you specified that your model be fit to `r names(config$inference$statistics)`, with some aggregation over period: `r unlist(config$inference$statistics)[which(stringr::str_detect(names(unlist(config$inference$statistics)), "period"))]`. 

```{r hosp_trajectories_inference_aggregate, results='asis', eval = inference}

  # for the single season to plot after full trajectory
    
  # plot_start_date <- as.Date("2008-09-01")
  # plot_end_date <- as.Date("2009-08-31")
  plot_start_date <- config$start_date
  plot_end_date <- config$end_date


  # get all outcome variables
  list_of_vars_config <- "config$outcomes$outcomes"
  outcomes <- eval(parse(text = list_of_vars_config))
  outcome_vars <- names(outcomes)
  fit_stats <- names(config$inference$statistics)
  # stat_list <- config$inference$statistics
  
  cat("\n\n")
  for(i in 1:length(fit_stats)){
    
    cat(paste0("### ",fit_stats[i]," {.tabset} \n"))
    
    statistics <- purrr::flatten(config$inference$statistics[i])
    cols_sim <- c("date", statistics$sim_var, "subpop","slot")
    cols_data <- c("date", "subpop", statistics$data_var)
    
    # aggregate based on what is in the config
    df_data <- lapply(node_names, function(y) {
      lapply(unique(hosp_outputs_global$slot), function(x)
        purrr::flatten_df(inference::getStats(
          hosp_outputs_global %>% .[subpop == y & slot == x],
          "date",
          "sim_var",
          stat_list = config$inference$statistics,
          start_date = config$start_date_groundtruth,
          end_date = config$end_date_groundtruth
        )) %>% dplyr::mutate(subpop = y, slot = x)) %>% dplyr::bind_rows() 
    }) %>% dplyr::bind_rows() 
    
    df_gt <- lapply(node_names, function(x) purrr::flatten_df(
      inference::getStats(
        gt_data %>% .[subpop == x],
        "date",
        "data_var",
        stat_list = config$inference$statistics,
        start_date = config$start_date_groundtruth,
        end_date = config$end_date_groundtruth
      )) %>% dplyr::mutate(subpop = x)) %>% dplyr::bind_rows()
    
    #   
    # df_data <- lapply(node_names, function(x) purrr::flatten_df(
    #   inference::getStats(
    #             hosp_outputs_global %>% .[subpop == x],
    #             "date",
    #             "data_var",
    #             stat_list = config$inference$statistics,
    #             start_date = config$start_date_groundtruth,
    #             end_date = config$end_date_groundtruth
    #         )) %>% dplyr::mutate(subpop = x)) %>% dplyr::bind_rows()
    
    ## Incident 
    cat(paste0("#### Incident \n"))
    print(
      df_data %>%
        setDT() %>%
        .[, date := lubridate::as_date(date)] %>%
        .[, .(date, subpop, sim_var, slot)] %>%
        .[slot == sim_sample] %>%
        data.table::melt(., id.vars = c("date", "slot", "subpop")) %>%
        ggplot() + 
        geom_line(aes(x = date, y = value)) + 
        # if inference, plot gt along side
        geom_point(data = df_gt,
                   aes(lubridate::as_date(date), data_var), color = 'firebrick', alpha = 0.1) +
        facet_wrap(~subpop, scales = 'free') +
        labs(x = 'date', y = statistics$name, title = "Incidence") +
        theme_classic() + theme_small
    )
    cat("\n\n")

    ## Cumulative
        cat(paste0("#### Cumulative \n"))
    print(
      df_data %>%
        setDT() %>%
        .[, date := lubridate::as_date(date)] %>%
        .[, .(date, subpop, sim_var, slot)] %>%
        .[slot == sim_sample] %>%
        data.table::melt(., id.vars = c("date", "slot", "subpop")) %>%
        # dplyr::arrange(subpop, slot, date) %>% 
        .[, csum := cumsum(value), by = .(slot, subpop, variable)] %>%
        ggplot() + 
        geom_line(aes(x = date, y = csum)) + 
        geom_point(data = df_gt %>% setDT() %>%
                     .[, csum := cumsum(data_var) , by = .(subpop)],
                   aes(lubridate::as_date(date), csum), color = 'firebrick', alpha = 0.1) +
        facet_wrap(~subpop, scales = 'free') + 
        labs(x = 'date', y = paste0("cumulative ", statistics$name), title = "Cumulative") +
        theme_classic()  + theme_small
    )
    cat("\n\n")
    
    ## Incident single season
    cat(paste0("#### Single season incidence \n"))
  
    print(
      df_data %>%
        setDT() %>%
        .[, date := lubridate::as_date(date)] %>%
        .[, .(date, subpop, sim_var, slot)] %>%
        .[slot == sim_sample] %>%
        data.table::melt(., id.vars = c("date", "slot", "subpop")) %>%
        dplyr::filter(date >= plot_start_date, date <= plot_end_date) %>%
        ggplot() + 
        geom_line(aes(x = date, y = value)) + 
        # if inference, plot gt along side
        geom_point(data = df_gt %>% dplyr::filter(date >= plot_start_date, date <= plot_end_date),
                   aes(lubridate::as_date(date), data_var), color = 'firebrick', alpha = 0.1) +
        facet_wrap(~subpop, scales = 'free') +
        labs(x = 'date', y = statistics$name, title = "Incidence") +
        theme_classic() + theme_small
    )
    
    cat("\n\n")

    ## Cumulative single season
        cat(paste0("#### Single season cumulative \n"))
    print(
      df_data %>%
        setDT() %>%
        .[, date := lubridate::as_date(date)] %>%
        .[, .(date, subpop, sim_var, slot)] %>%
        .[slot == sim_sample] %>%
        data.table::melt(., id.vars = c("date", "slot", "subpop")) %>% 
        dplyr::filter(date >= plot_start_date, date <= plot_end_date)%>%
        # dplyr::arrange(subpop, slot, date) %>% 
        .[, csum := cumsum(value), by = .(slot, subpop, variable)] %>%
        ggplot() + 
        geom_line(aes(x = date, y = csum)) + 
        geom_point(data = df_gt %>% setDT() %>% 
                     dplyr::filter(date >= plot_start_date, date <= plot_end_date) %>%
                     .[, csum := cumsum(data_var) , by = .(subpop)],
                   aes(lubridate::as_date(date), csum), color = 'firebrick', alpha = 0.1) +
        facet_wrap(~subpop, scales = 'free') + 
        labs(x = 'date', y = paste0("cumulative ", statistics$name), title = "Cumulative") +
        theme_classic()  + theme_small
    )
    
  }
  cat("\n\n")


```

## Inference specific outcomes: aggregated quantiles {.tabset}
```{r hosp_aggregate_quantiles, results='asis', eval = inference}

if(length(unique(hosp_outputs_global$slot)) > 1 & inference){

  cat("\n\n")
  for(i in 1:length(fit_stats)){
    
    cat(paste0("### ",fit_stats[i]," {.tabset} \n"))
    statistics <- purrr::flatten(config$inference$statistics[i])
    
    # Incident
            cat(paste0("#### Incident \n"))
    print(
      df_data %>%
        setDT() %>%
        .[, date := lubridate::as_date(date)] %>%
        .[, as.list(quantile(sim_var, c(.05, .25, .5, .75, .95), na.rm = TRUE, names = FALSE)), by = c("date", "subpop")] %>%
        setnames(., paste0("V", 1:5), paste0("q", c(.05,.25,.5,.75,.95))) %>%
        ggplot() + 
        geom_ribbon(aes(x = date, ymin = q0.05, ymax = q0.95), alpha = 0.1) +
        geom_ribbon(aes(x = date, ymin = q0.25, ymax = q0.75), alpha = 0.1) +
        geom_line(aes(x = date, y = q0.5)) + 
        # if inference, plot gt along side
        geom_point(data = df_gt,
                   aes(lubridate::as_date(date), data_var), color = 'firebrick', alpha = 0.1) +
        facet_wrap(~subpop, scales = 'free') +
        # facet_wrap(~get(subpop), scales = 'free') +
        labs(x = 'date', y = statistics$name) +
        theme_classic() + theme_small
    )
    
    ## Cumulative
    cat("\n\n")
    cat(paste0("#### Cumulative \n"))

    print(
      df_data %>%
        setDT() %>%
        .[, date := lubridate::as_date(date)] %>%
        .[, .(date, subpop, sim_var, slot)] %>%
        data.table::melt(., id.vars = c("date", "slot", "subpop")) %>%
        # dplyr::arrange(subpop, slot, date) %>% 
        .[, csum := cumsum(value), by = .(slot, subpop, variable)] %>%
        .[, as.list(quantile(csum, c(.05, .25, .5, .75, .95), na.rm = TRUE, names = FALSE)), by = c("date", config$subpop_setup$subpop)] %>%
        setnames(., paste0("V", 1:5), paste0("q", c(.05,.25,.5,.75,.95))) %>%
        ggplot() + 
        geom_ribbon(aes(x = date, ymin = q0.05, ymax = q0.95), alpha = 0.1) +
        geom_ribbon(aes(x = date, ymin = q0.25, ymax = q0.75), alpha = 0.1) +
        geom_line(aes(x = date, y = q0.5)) + 
        geom_point(data = df_gt %>% setDT() %>%
                     .[, csum := cumsum(data_var) , by = .(subpop)],
                   aes(lubridate::as_date(date), csum), color = 'firebrick', alpha = 0.1) +
        facet_wrap(~subpop, scales = 'free') +
        # facet_wrap(~get(subpop), scales = 'free') +      
        labs(x = 'date', y = paste0("cumulative ", statistics$name)) +
        theme_classic() + theme_small
    )
    
  }
    cat("\n\n")

}

```


## Hosp by likelihood

Trajectories of the 5 and bottom 5 log likelihoods for each subpopulation. 

```{r hosp_trajectories_by_likelihood,results='hide',fig.keep='all', eval=inference}


for(i in 1:length(fit_stats)){
  statistics <- purrr::flatten(config$inference$statistics[i])
  cols_sim <- c("date", statistics$sim_var, config$subpop_setup$subpop,"slot")
  cols_data <- c("date", config$subpop_setup$subpop, statistics$data_var)
  if(exists("llik")){
    llik_rank <- llik %>% 
      .[, .SD[order(ll)], subpop] 
    high_low_llik <- rbindlist(list(data.table(llik_rank, key = "subpop") %>%
                                      .[, head(.SD,5), by = "subpop"] %>% 
                                      .[, llik_bin := "top"], 
                                    data.table(llik_rank, key = "subpop") %>%
                                      .[, tail(.SD,5), by = "subpop"]%>% 
                                      .[, llik_bin := "bottom"])
    )
    
    high_low_hosp_llik <- hosp_outputs_global %>% 
      .[high_low_llik, on = c("slot", "subpop"), allow.cartesian=TRUE]
    
    hosp_llik_plots <- lapply(unique(high_low_hosp_llik %>% .[, subpop]),
                              function(e){
                                high_low_hosp_llik %>%
                                  .[, date := lubridate::as_date(date)] %>%
                                  .[subpop == e] %>%
                                  ggplot() +
                                  geom_line(aes(lubridate::as_date(date), get(statistics$sim_var),
                                                group = slot, color = ll)) + #, linetype = llik_bin
                                  scale_linetype_manual(values = c(1, 2), name = "likelihood\nbin") +
                                  scale_color_viridis_c(option = "D", name = "log\nlikelihood") +
                                  {if(inference & outcome_vars_[i] %in% colnames(gt_data))
                                    geom_point(data = gt_data %>% .[, .(date,subpop, value = get(statistics$data_var))],
                                               aes(lubridate::as_date(date), value), color = 'firebrick', alpha = 0.1)
                                  } +
                                  facet_wrap(~subpop, scales = 'free') +
                                  guides(linetype = 'none') +
                                  labs(x = 'date', y = fit_stats[i]) + #, title = paste0("top 5, bottom 5 lliks, ", statistics$sim_var)) +
                                  theme_classic() + theme_small +
                                  theme(legend.key.size = unit(0.2, "cm"))
                              }
    )
    
    if(length(hosp_llik_plots) != 1){
      print(do.call("grid.arrange", c(hosp_llik_plots, ncol=2)))
    }else{
      print(hosp_llik_plots[[1]])
    }
    
  }
}


```




## Parameters perturbing over time
### SEIR parameter modifiers - SNPI


```{r snpi_evolution, results='hide',fig.keep='all', eval=inference}

snpi_outputs_chimeric_int <- setDT(import_model_outputs(scenario_run_dir, inference,  "snpi", 'chimeric', 'intermediate'))

llik_outputs_chimeric_int <- setDT(import_model_outputs(scenario_run_dir, inference,  "llik", 'chimeric', 'intermediate'))

snpi_llik_chimeric_int <- snpi_outputs_chimeric_int %>% .[llik_outputs_chimeric_int, on = .(subpop, slot, block, iter)] %>%
  .[, iter_name := ifelse(is.na(iter), "F", iter)]

snpi_llik_chimeric_int %>% 
  ggplot() + 
  geom_line(aes(iter,reduction, group = slot)) +
  geom_point(aes(iter, reduction, colour = ll)) +
  facet_grid(subpop ~ npi_name, scales = 'free_y') + 
  scale_color_viridis_c(option = "B", name = "log\nlikelihood") +
  theme_bw() + theme_small


```



### Outcome parameter modifiers - HNPI

```{r hnpi_evolution, results='hide',fig.keep='all', eval=inference}

hnpi_outputs_chimeric_int <- setDT(import_model_outputs(scenario_run_dir, inference,  "hnpi", 'chimeric', 'intermediate'))

llik_outputs_chimeric_int <- setDT(import_model_outputs(scenario_run_dir, inference,  "llik", 'chimeric', 'intermediate'))

hnpi_llik_chimeric_int <- hnpi_outputs_chimeric_int %>% .[llik_outputs_chimeric_int, on = .(subpop, slot, block, iter)] %>%
  .[, iter_name := ifelse(is.na(iter), "F", iter)]

hnpi_llik_chimeric_int %>% 
  ggplot() + 
  geom_line(aes(iter,reduction, group = slot)) +
  geom_point(aes(iter, reduction, colour = ll)) +
  facet_grid(subpop ~ npi_name, scales = 'free_y') + 
  theme_bw() + theme_small


```






