---
title: "Model Output plots"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document: 
    toc: true
    toc_depth: 2
    number_sections: TRUE
    keep_tex: FALSE
params:
  opt: !r option_list = list(optparse::make_option(c("-c", "--config"), action="store", default=Sys.getenv("CONFIG_PATH", Sys.getenv("CONFIG_PATH")), type='character', help="path to the config file"), optparse::make_option(c("-d", "--data_path"), action="store", default=Sys.getenv("DATA_PATH", Sys.getenv("DATA_PATH")), type='character', help="path to the data repo"), optparse::make_option(c("-u","--run-id"), action="store", dest = "run_id", type='character', help="Unique identifier for this run", default = Sys.getenv("FLEPI_RUN_INDEX",flepicommon::run_id())),  optparse::make_option(c("-R", "--results-path"), action="store", dest = "results_path",  type='character', help="Path for model output", default = Sys.getenv("FS_RESULTS_PATH", Sys.getenv("FS_RESULTS_PATH"))))
---

```{r setup, include=FALSE}
suppressMessages(library(parallel))
suppressMessages(library(foreach))
suppressMessages(library(inference))
suppressMessages(library(tidyverse))
suppressMessages(library(tidyr))
suppressMessages(library(doParallel))
suppressMessages(library(dplyr))
suppressMessages(library(data.table))
suppressMessages(library(ggplot2))
suppressMessages(library(ggforce))
suppressMessages(library(ggforce))
suppressMessages(library(gridExtra))

parser=optparse::OptionParser(option_list=params$opt)
opt = optparse::parse_args(parser, convert_hyphens_to_underscores = TRUE)

knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE,
	cache = TRUE,
	cache.lazy = FALSE
)
# knitr::opts_knit$set(root.dir = opt$data_path)

```

```{r data-setup}


# FUNCTIONS ---------------------------------------------------------------

import_model_outputs <-
  function(scn_dir,
           outcome,
           global_opt,
           final_opt,
           lim_hosp = c("date",
                        "incidH",
                        "incidC",
                        "incidD",
                        # lim_hosp = c("date",
                        #              sapply(1:length(names(config$inference$statistics)), function(i) purrr::flatten(config$inference$statistics[i])$sim_var),
                        config$spatial_setup$nodenames)) {
    # "subpop")){
    dir_ <- paste0(
      scn_dir,
      "/",
      outcome,
      "/",
      config$name,
      "/",
      config$interventions$scenarios,
      "/",
      config$outcomes$scenarios
    )
    subdir_ <- paste0(dir_, "/", list.files(dir_),
                      "/",
                      global_opt,
                      "/",
                      final_opt)
    subdir_list <- list.files(subdir_)
    
    out_ <- NULL
    total <- length(subdir_list)
    
    print(paste0("Importing ", outcome, " files (n = ", total, "):"))
    
    for (i in 1:length(subdir_list)) {
      if (any(grepl("parquet", subdir_list))) {
        dat <-
          arrow::read_parquet(paste(subdir_, subdir_list[i], sep = "/"))
      }
      if (outcome == "hosp") {
        dat <-
          arrow::read_parquet(paste(subdir_, subdir_list[i], sep = "/")) %>%
          select(all_of(lim_hosp))
      }
      if (any(grepl("csv", subdir_list))) {
        dat <- read.csv(paste(subdir_, subdir_list[i], sep = "/"))
      }
      if (final_opt == "final") {
        dat$slot <- as.numeric(str_sub(subdir_list[i], start = 1, end = 9))
      }
      if (final_opt == "intermediate") {
        dat$slot <- as.numeric(str_sub(subdir_list[i], start = 1, end = 9))
        dat$block <-
          as.numeric(str_sub(subdir_list[i], start = 11, end = 19))
      }
      out_ <- rbind(out_, dat)
      
    }
    return(out_)
  }

config <- flepicommon::load_config(opt$config)

res_dir <- file.path(opt$results_path, config$model_output_dirname)
print(res_dir)

```

```{r read-in-model-output, cache = TRUE}
# Pull in subpop data
geodata <-
  setDT(read.csv(file.path(
    config$data_path, config$spatial_setup$geodata
  )))
# geodata <- setDT(read.csv(file.path(config$data_path, config$subpop_setup$geodata)))


## gt_data MUST exist directly after a run (ONLY IF INFERENCE RUN)
if (!is.null(config$inference)) {
  gt_data <- data.table::fread(config$inference$gt_data_path) %>%
    .[, subpop := stringr::str_pad(FIPS,
                                   width = 5,
                                   side = "left",
                                   pad = "0")]
}

if (!is.null(config$inference)) {
  inference <- TRUE
} else{
  inference <- FALSE
}

theme_small <-
  theme(
    text = element_text(size = 8),
    strip.background = element_blank(),
    strip.placement = "outside"
  )

```
📸

Here is a snapshot of your model outputs for run ID `r opt$run_id`, from config `r opt$config`, stored in `r opt$results_path`. 

# Infection model: SEIR model output

```{r seir, cache = TRUE, fig.dim = c(8, 20), results='hide',fig.keep='all'}
# read in model outputs
seir_outputs_global <-
  setDT(import_model_outputs(res_dir, "seir", 'global', 'final'))

# get different aggregation from list of config compartments?
## assuming there is always infection_stage, aggregate over this, incorporate aggregation of other variables later TO DO
## assume always interested in prevalence

# if(inference){group_by_cols <- c("mc_infection_stage", "mc_value_type","slot","date")}else{group_by_cols <- c("mc_infection_stage","mc_value_type","date")}
group_by_cols <-
  c("mc_infection_stage", "mc_value_type", "slot", "date") # I think if just one slot, gets read in as slot = 1?
subpop_cols <-
  colnames(seir_outputs_global)[!str_detect(colnames(seir_outputs_global), "mc")]
subpop_cols <-
  subpop_cols[which(!subpop_cols %in% c("date", "slot"))]

tmp_seir <- seir_outputs_global %>%
  .[, lapply(.SD, sum, na.rm = TRUE), by = group_by_cols, .SDcols = subpop_cols]

# plot an example simulation
print(
  tmp_seir %>% .[mc_value_type == "prevalence" &
                   slot == sample(unique(tmp_seir$slot), 1)] %>%
    data.table::melt(., measure.vars = subpop_cols) %>%
    ggplot() +
    geom_line(aes(date, value, colour = mc_infection_stage)) +
    facet_wrap(
      ~ variable,
      scales = 'free',
      ncol = 4,
      strip.position = "right"
    ) +
    theme_classic() +
    theme(legend.position = "bottom") + 
    theme_small
)
```


# Infection model: SNPI model output

```{r snpi, cache = TRUE, fig.dim = c(8,20), results='hide',fig.keep='all'}
# read in model outputs
snpi_outputs_global <- setDT(import_model_outputs(res_dir, "snpi", 'global', 'final'))
node_names <- unique(snpi_outputs_global %>% .[ , get(config$spatial_setup$nodenames)])
# node_names <- unique(sort(snpi_outputs_global %>% .[ , "subpop"]))
node_names <- c(node_names[str_detect(node_names,",")], node_names[!str_detect(node_names,",")]) # sort so that multiple subpops are in front

if(inference){
  llik <- setDT(import_model_outputs(res_dir, "llik", 'global', 'final'))
  # snpi_outputs_global <- snpi_outputs_global %>%
  #   .[llik, on = c("geoid", "slot")] 
}

snpi_plots <- lapply(node_names,
                     function(i){
                       if(!grepl(',', i)){
                         snpi_outputs_global %>%
                           {if(inference)
                             .[llik, on = c("geoid", "slot")] } %>%
                           .[geoid == i] %>%
                           ggplot(aes(npi_name,reduction)) + 
                           geom_violin() + 
                           {if(inference)
                             geom_jitter(aes(group = npi_name, color = ll), size = 0.5, height = 0, width = 0.2, alpha = 0.5) 
                           } +
                           {if(!inference)
                             geom_jitter(aes(group = npi_name), size = 0.5, height = 0, width = 0.2, alpha = 0.5) 
                           } + 
                           theme_bw(base_size = 10) +
                           theme(axis.text.x = element_text(angle = 60, hjust = 1, size = 6),
                                 text = element_text(size = 8)) +  
                               guides(color = guide_legend(override.aes = list(size = 0.5)))+
                           scale_color_viridis_c(option = "B", name = "log\nlikelihood") +
                           labs(x = "parameter", title = i) + theme_small
                         
                       }else{
                         if(inference){
                           nodes_ <- unlist(strsplit(i,","))
                           ll_across_nodes <- 
                             llik %>% 
                             .[geoid %in% nodes_] %>%
                             .[, .(ll_sum = sum(ll)), by = .(slot)]
                         }
                         
                         snpi_outputs_global %>%
                           {if(inference)
                             .[ll_across_nodes, on = c("slot")]} %>%
                           .[geoid == i] %>%
                           ggplot(aes(npi_name,reduction)) + 
                           geom_violin() + 
                           {if(inference)
                             geom_jitter(aes(group = npi_name, color = ll_sum), size = 0.5, height = 0, width = 0.2, alpha = 0.5)
                           } +
                           {if(!inference)
                             geom_jitter(aes(group = npi_name), size = 0.5, height = 0, width = 0.2, alpha = 0.5)
                           } + 
                           theme_bw(base_size = 10) +
                           theme(axis.text.x = element_text(angle = 60, hjust = 1, size = 6),
                                 text = element_text(size = 8)) +  
                               guides(color = guide_legend(override.aes = list(size = 0.5)))+
                           scale_color_viridis_c(option = "B", name = "log\nlikelihood") +
                           labs(x = "parameter") + theme_small
                       }
                     }
)

print(do.call("grid.arrange", c(snpi_plots, ncol=4)))

```


#Outcome model: HOSP model output
<!-- if NO inference, just plot hosp at daily - all aggregate outcomes (?) -->
<!-- if inference, plot hosp with gt at daily, and at fitting aggregation - ONLY stats in the inference section? -->
<!-- cumulatives and incident for all? -->
<!-- plot quantiles and some sample trajectories as well -->

## Daily hosp {.tabset}
### Single trajectories {.tabset}
```{r hosp_daily_single_slot, results='asis', cache = TRUE, fig.dim = c(8,8)}
## add something so that if it doesn't exist, it prints some 'no output' message

# get all outcome variables
scns <- config$outcomes$scenarios
list_of_vars_config <- paste0("config$outcomes$settings$", scns)
outcomes <- eval(parse(text = list_of_vars_config))
outcome_vars <- names(outcomes)

# for simplicity, get aggregate outcome variables
outcome_vars_ <- outcome_vars[!str_detect(outcome_vars, "_")]

# read in model outputs
hosp_outputs_global <- setDT(import_model_outputs(res_dir, "hosp", 'global', 'final',
                                                  lim_hosp = c("date", config$spatial_setup$nodenames, outcome_vars_)))
# lim_hosp = c("date", "subpop", outcome_vars_)))
# num_nodes <- length(unique(hosp_outputs_global %>% .[,"subpop"])) 
num_nodes <- length(unique(hosp_outputs_global %>% .[,get(config$spatial_setup$nodenames)]))

sim_sample <- sample(unique(hosp_outputs_global$slot),1)


cat("\n\n")

## plot ONE sample trajectory for sanity check (can modify) 
for(i in 1:length(outcome_vars_)){
  
  cat(paste0("#### ",outcome_vars_[i]," \n"))
  
  ## Incident 
  print(
    hosp_outputs_global %>%
      .[, date := lubridate::as_date(date)] %>%
      .[, .(date, geoid, outcome = get(outcome_vars_[i]), slot)] %>%
      .[slot == sim_sample] %>%
      data.table::melt(., id.vars = c("date", "slot", "geoid")) %>%
      # data.table::melt(., id.vars = c("date", "slot", "subpop")) %>%
      ggplot() + 
      geom_line(aes(x = date, y = value)) + 
      # if inference, plot gt along side
      {if(inference & outcome_vars_[i] %in% colnames(gt_data))
        if(any(!is.na(gt_data %>% .[, get(outcome_vars_[i])])))
          geom_point(data = gt_data %>% .[, .(date, geoid = subpop, value = get(outcome_vars_[i]))],
                     aes(lubridate::as_date(date), value), color = 'firebrick', alpha = 0.1)
      } +
      # facet_wrap(~subpop, scales = 'free') +
      facet_wrap(~get(config$spatial_setup$nodenames), scales = 'free') +
      labs(x = 'date', y = outcome_vars_[i], title = "Incidence") +
      theme_classic() + theme_small
  )
  
  ## Cumulative
  print(
    hosp_outputs_global %>%
      .[, date := lubridate::as_date(date)] %>%
      .[, .(date, geoid, outcome = get(outcome_vars_[i]), slot)] %>%
      .[slot == sim_sample] %>% 
      data.table::melt(., id.vars = c("date", "slot", "geoid")) %>%
      # dplyr::arrange(geoid, slot, date) %>% 
      .[, csum := cumsum(value), by = .(slot, geoid, variable)] %>%
      ggplot() + 
      geom_line(aes(x = date, y = csum)) + 
      {if(inference & outcome_vars_[i] %in% colnames(gt_data))
        geom_point(data = gt_data %>% .[, .(date, geoid = subpop, value = get(outcome_vars_[i]))] %>%
                     .[, csum := cumsum(value) , by = .(geoid)],
                   aes(lubridate::as_date(date), csum), color = 'firebrick', alpha = 0.1) 
      } +
      # facet_wrap(~subpop, scales = 'free') +      
      facet_wrap(~get(config$spatial_setup$nodenames), scales = 'free') +      
      labs(x = 'date', y = paste0("cumulative ", outcome_vars_[i]), title = "Cumulative") +
      theme_classic() + theme_small
  )
  
  
  cat("\n\n")
  
}

```

### Quantiles {.tabset}
```{r hosp_daily_quantiles, results='asis', cache = TRUE, fig.dim = c(8,8)}
# ```{r hosp_daily_quantiles, fig.dim = c(8,8), results='hide',fig.keep='all'}

if(length(unique(hosp_outputs_global$slot)) > 1){
  
  cat("\n\n")
  
  ## plot quantiles (if more than one slot)
  for(i in 1:length(outcome_vars_)){
    
    cat(paste0("#### ",outcome_vars_[i]," \n"))
    ## plot quantiles (if more than one slot)
    # for(i in 1:length(outcome_vars_)){
    
    # incident
    print(
      hosp_outputs_global %>%
        .[, date := lubridate::as_date(date)] %>%
        # .[, as.list(quantile(get(outcome_vars_[i]), c(.05, .25, .5, .75, .95), na.rm = TRUE, names = FALSE)), by = c("date", "subpop")] %>%
        .[, as.list(quantile(get(outcome_vars_[i]), c(.05, .25, .5, .75, .95), na.rm = TRUE, names = FALSE)), by = c("date", config$spatial_setup$nodenames)] %>%
        setnames(., paste0("V", 1:5), paste0("q", c(.05,.25,.5,.75,.95))) %>%
        ggplot() + 
        geom_ribbon(aes(x = date, ymin = q0.05, ymax = q0.95), alpha = 0.1) +
        geom_ribbon(aes(x = date, ymin = q0.25, ymax = q0.75), alpha = 0.1) +
        geom_line(aes(x = date, y = q0.5)) + 
        # if inference, plot gt along side
        {if(inference & outcome_vars_[i] %in% colnames(gt_data))
          if(any(!is.na(gt_data %>% .[, get(outcome_vars_[i])])))
            geom_point(data = gt_data %>% .[, .(date, geoid = subpop, value = get(outcome_vars_[i]))],
                       aes(lubridate::as_date(date), value), color = 'firebrick', alpha = 0.1)
        } +
        # facet_wrap(~subpop, scales = 'free') +
        facet_wrap(~get(config$spatial_setup$nodenames), scales = 'free') +
        labs(x = 'date', y = outcome_vars_[i], title = "Incidence") +
        theme_classic()+ theme_small
    )
    
    # cumulative
    print(
      hosp_outputs_global %>%
        .[, date := lubridate::as_date(date)] %>%
        .[, .(date, geoid, outcome = get(outcome_vars_[i]), slot)] %>%
        data.table::melt(., id.vars = c("date", "slot", "geoid")) %>%
        # dplyr::arrange(geoid, slot, date) %>% 
        .[, csum := cumsum(value), by = .(slot, geoid, variable)] %>%
        .[, as.list(quantile(csum, c(.05, .25, .5, .75, .95), na.rm = TRUE, names = FALSE)), by = c("date", "geoid")] %>%
        setnames(., paste0("V", 1:5), paste0("q", c(.05,.25,.5,.75,.95))) %>%
        ggplot() + 
        geom_ribbon(aes(x = date, ymin = q0.05, ymax = q0.95), alpha = 0.1) +
        geom_ribbon(aes(x = date, ymin = q0.25, ymax = q0.75), alpha = 0.1) +
        geom_line(aes(x = date, y = q0.5)) + 
        {if(inference & outcome_vars_[i] %in% colnames(gt_data))
          geom_point(data = gt_data %>% .[, .(date, geoid = subpop, value = get(outcome_vars_[i]))] %>%
                       .[, csum := cumsum(value) , by = .(geoid)],
                     aes(lubridate::as_date(date), csum), color = 'firebrick', alpha = 0.1) 
        } +
        # facet_wrap(~subpop, scales = 'free') +      
        facet_wrap(~get(config$spatial_setup$nodenames), scales = 'free') +
        labs(x = 'date', y = paste0("cumulative ", outcome_vars_[i]), title = "Cumulative") +
        theme_classic() + theme_small
    )
    
  }
  cat("\n\n")
  
}

```




# Outcome model: HNPI model output

```{r hnpi, cache = TRUE, fig.dim = c(8,20), results='hide',fig.keep='all'}
# read in model outputs
hnpi_outputs_global <- setDT(import_model_outputs(res_dir, "hnpi", 'global', 'final'))
node_names <- unique(hnpi_outputs_global %>% .[ , get(config$spatial_setup$nodenames)])
# node_names <- unique(sort(hnpi_outputs_global %>% .[ , "subpop"]))
node_names <- c(node_names[str_detect(node_names,",")], node_names[!str_detect(node_names,",")]) # sort so that multiple subpops are in front

if(inference){
  llik <- setDT(import_model_outputs(res_dir, "llik", 'global', 'final'))
}


hnpi_plots <- lapply(node_names,
                     function(i){
                       hnpi_outputs_global %>%
                         .[llik, on = c("geoid", "slot")] %>%
                         .[geoid == i] %>%
                         ggplot(aes(npi_name,reduction)) + 
                         geom_violin() +
                         {if(inference)
                           geom_jitter(aes(group = npi_name, colour = ll), size = 0.6, height = 0, width = 0.2, alpha = 1) 
                         } +
                         {if(!inference)
                           geom_jitter(aes(group = npi_name), size = 0.6, height = 0, width = 0.2, alpha = 1)
                         } + 
                         facet_wrap(~geoid, scales = 'free') +
                             guides(color = guide_legend(override.aes = list(size = 0.5))) +
                         scale_color_viridis_c(option = "B", name = "log\nlikelihood") +
                         theme_classic()+ theme_small
                     }
)
print(do.call("grid.arrange", c(hnpi_plots, ncol=4)))

```

# Inference: analyses
## Likelihood 
```{r llik_acceptances}

```


## Inference specific outcomes: aggregated {.tabset}
### Single trajectories (aggregated by fitting) {.tabset}
```{r hosp_trajectories_inference_aggregate, fig.dim = c(8,20), results='hide',fig.keep='all'}
if(inference){
  # get all outcome variables
  scns <- config$outcomes$scenarios
  list_of_vars_config <- paste0("config$outcomes$settings$", scns)
  outcomes <- eval(parse(text = list_of_vars_config))
  outcome_vars <- names(outcomes)
  fit_stats <- names(config$inference$statistics)
  # stat_list <- config$inference$statistics
  
  cat("\n\n")
  for(i in 1:length(fit_stats)){
    
    cat(paste0("#### ",fit_stats[i]," \n"))
    
    statistics <- purrr::flatten(config$inference$statistics[i])
    cols_sim <- c("date", statistics$sim_var, "geoid","slot")
    cols_data <- c("date", "subpop", statistics$data_var)
    
    # aggregate based on what is in the config
    df_data <- lapply(node_names, function(y) {
      lapply(unique(hosp_outputs_global$slot), function(x)
        purrr::flatten_df(inference::getStats(
          hosp_outputs_global %>% .[geoid == y & slot == x],
          "date",
          "sim_var",
          stat_list = config$inference$statistics,
          start_date = config$start_date_groundtruth,
          end_date = config$end_date_groundtruth
        )) %>% dplyr::mutate(geoid = y, slot = x)) %>% dplyr::bind_rows() 
    }) %>% dplyr::bind_rows() 
    
    df_gt <- lapply(node_names, function(x) purrr::flatten_df(
      inference::getStats(
        gt_data %>% .[subpop == x],
        "date",
        "data_var",
        stat_list = config$inference$statistics,
        start_date = config$start_date_groundtruth,
        end_date = config$end_date_groundtruth
      )) %>% dplyr::mutate(geoid = x)) %>% dplyr::bind_rows()
    
    #   
    # df_data <- lapply(node_names, function(x) purrr::flatten_df(
    #   inference::getStats(
    #             hosp_outputs_global %>% .[geoid == x],
    #             "date",
    #             "data_var",
    #             stat_list = config$inference$statistics,
    #             start_date = config$start_date_groundtruth,
    #             end_date = config$end_date_groundtruth
    #         )) %>% dplyr::mutate(geoid = x)) %>% dplyr::bind_rows()
    
    ## Incident 
    print(
      df_data %>%
        setDT() %>%
        .[, date := lubridate::as_date(date)] %>%
        .[, .(date, geoid, sim_var, slot)] %>%
        .[slot == sim_sample] %>%
        data.table::melt(., id.vars = c("date", "slot", "geoid")) %>%
        # data.table::melt(., id.vars = c("date", "slot", "subpop")) %>%
        ggplot() + 
        geom_line(aes(x = date, y = value)) + 
        # if inference, plot gt along side
        geom_point(data = df_gt,
                   aes(lubridate::as_date(date), data_var), color = 'firebrick', alpha = 0.1) +
        # facet_wrap(~subpop, scales = 'free') +
        facet_wrap(~get(config$spatial_setup$nodenames), scales = 'free') +
        labs(x = 'date', y = statistics$name, title = "Incidence") +
        theme_classic() + theme_small
    )
    
    ## Cumulative
    print(
      df_data %>%
        setDT() %>%
        .[, date := lubridate::as_date(date)] %>%
        .[, .(date, geoid, sim_var, slot)] %>%
        .[slot == sim_sample] %>%
        data.table::melt(., id.vars = c("date", "slot", "geoid")) %>%
        # dplyr::arrange(geoid, slot, date) %>% 
        .[, csum := cumsum(value), by = .(slot, geoid, variable)] %>%
        ggplot() + 
        geom_line(aes(x = date, y = csum)) + 
        geom_point(data = df_gt %>% setDT() %>%
                     .[, csum := cumsum(data_var) , by = .(geoid)],
                   aes(lubridate::as_date(date), csum), color = 'firebrick', alpha = 0.1) +
        # facet_wrap(~subpop, scales = 'free') +      
        facet_wrap(~get(config$spatial_setup$nodenames), scales = 'free') +   
        labs(x = 'date', y = paste0("cumulative ", statistics$name), title = "Cumulative") +
        theme_classic()  + theme_small
    )
    
  }
  cat("\n\n")
  
}

```

### Quantiles(aggregated by fitting) {.tabset}
```{r hosp_aggregate_quantiles, fig.dim = c(8,20), results='hide',fig.keep='all'}

if(length(unique(hosp_outputs_global$slot)) > 1 & inference){

  cat("\n\n")
  for(i in 1:length(fit_stats)){
    
    cat(paste0("#### ",fit_stats[i]," \n"))
    statistics <- purrr::flatten(config$inference$statistics[i])
    
    # Incident
    print(
      df_data %>%
        setDT() %>%
        .[, date := lubridate::as_date(date)] %>%
        .[, as.list(quantile(sim_var, c(.05, .25, .5, .75, .95), na.rm = TRUE, names = FALSE)), by = c("date", "geoid")] %>%
        setnames(., paste0("V", 1:5), paste0("q", c(.05,.25,.5,.75,.95))) %>%
        ggplot() + 
        geom_ribbon(aes(x = date, ymin = q0.05, ymax = q0.95), alpha = 0.1) +
        geom_ribbon(aes(x = date, ymin = q0.25, ymax = q0.75), alpha = 0.1) +
        geom_line(aes(x = date, y = q0.5)) + 
        # if inference, plot gt along side
        geom_point(data = df_gt,
                   aes(lubridate::as_date(date), data_var), color = 'firebrick', alpha = 0.1) +
        # facet_wrap(~subpop, scales = 'free') +
        facet_wrap(~get(config$spatial_setup$nodenames), scales = 'free') +
        labs(x = 'date', y = statistics$name) +
        theme_classic() + theme_small
    )
    
    ## Cumulative
    print(
      df_data %>%
        setDT() %>%
        .[, date := lubridate::as_date(date)] %>%
        .[, .(date, geoid, sim_var, slot)] %>%
        data.table::melt(., id.vars = c("date", "slot", "geoid")) %>%
        # dplyr::arrange(geoid, slot, date) %>% 
        .[, csum := cumsum(value), by = .(slot, geoid, variable)] %>%
        .[, as.list(quantile(csum, c(.05, .25, .5, .75, .95), na.rm = TRUE, names = FALSE)), by = c("date", config$subpop_setup$subpop)] %>%
        setnames(., paste0("V", 1:5), paste0("q", c(.05,.25,.5,.75,.95))) %>%
        ggplot() + 
        geom_ribbon(aes(x = date, ymin = q0.05, ymax = q0.95), alpha = 0.1) +
        geom_ribbon(aes(x = date, ymin = q0.25, ymax = q0.75), alpha = 0.1) +
        geom_line(aes(x = date, y = q0.5)) + 
        geom_point(data = df_gt %>% setDT() %>%
                     .[, csum := cumsum(data_var) , by = .(geoid)],
                   aes(lubridate::as_date(date), csum), color = 'firebrick', alpha = 0.1) +
        # facet_wrap(~subpop, scales = 'free') +      
        facet_wrap(~get(config$spatial_setup$nodenames), scales = 'free') +      
        labs(x = 'date', y = paste0("cumulative ", statistics$name)) +
        theme_classic() + theme_small
    )
    
  }
    cat("\n\n")

}

```


## Hosp by likelihood

Trajectories of the 5 and bottom 5 log likelihoods for each subpopulation. 

```{r hosp_trajectories_by_likelihood, fig.dim = c(8,20), results='hide',fig.keep='all'}

if(inference){
  
  for(i in 1:length(fit_stats)){
    statistics <- purrr::flatten(config$inference$statistics[i])
    cols_sim <- c("date", statistics$sim_var, config$subpop_setup$subpop,"slot")
    cols_data <- c("date", config$subpop_setup$subpop, statistics$data_var)
    if(exists("llik")){
      llik_rank <- llik %>% 
        .[, .SD[order(ll)], geoid] 
      high_low_llik <- rbindlist(list(data.table(llik_rank, key = eval(config$spatial_setup$nodenames)) %>%
                                        .[, head(.SD,5), by = eval(config$spatial_setup$nodenames)] %>% 
                                        .[, llik_bin := "top"], 
                                      data.table(llik_rank, key = eval(config$spatial_setup$nodenames)) %>%
                                        .[, tail(.SD,5), by = eval(config$spatial_setup$nodenames)]%>% 
                                        .[, llik_bin := "bottom"])
      )
      
      high_low_hosp_llik <- hosp_outputs_global %>% 
        .[high_low_llik, on = c("slot", eval(config$spatial_setup$nodenames))]
      
      hosp_llik_plots <- lapply(unique(high_low_hosp_llik %>% .[, geoid]),
                                function(e){
                                  high_low_hosp_llik %>%
                                    .[, date := lubridate::as_date(date)] %>%
                                    # { if(config$subpop_setup$subpop == 'subpop'){
                                    #   .[geodata %>% .[, subpop := stringr::str_pad(subpop, width = 5, side = "left", pad = "0")], on = .(subpop)]}
                                    # } %>%
                                    .[geoid == e] %>%
                                    # { if(config$subpop_setup$subpop == 'subpop'){ .[, subpop := USPS]}
                                    # } %>%
                                    ggplot() +
                                    geom_line(aes(lubridate::as_date(date), get(statistics$data_var),
                                                  group = slot, color = ll, linetype = llik_bin)) +
                                    scale_linetype_manual(values = c(1, 2), name = "likelihood\nbin") +
                                    scale_color_viridis_c(option = "D", name = "log\nlikelihood") +
                                    {if(inference & outcome_vars_[i] %in% colnames(gt_data))
                                      geom_point(data = gt_data %>% .[, .(date, geoid = subpop, value = get(outcome_vars_[i]))],
                                                 aes(lubridate::as_date(date), value), color = 'firebrick', alpha = 0.1)
                                    } +
                                    facet_wrap(~geoid, scales = 'free') +
                                    guides(color = guide_legend(override.aes = list(size = 0.5)), 
                                           linetype = 'none') +
                                    labs(x = 'date', y = fit_stats[i]) + #, title = paste0("top 5, bottom 5 lliks, ", statistics$sim_var)) +
                                    theme_classic() + theme_small 
                                }
      )
      
      print(do.call("grid.arrange", c(hosp_llik_plots, ncol=4)))

    }
  }
}


```





